Figure Extra

### 2023-07-31 Figures/Figures_nonTCGA.Rmd
change naming script from Thomas RNAseq to Nakamura2018

# Thomas RNAseq #! Change name!
## Data loading
```{r}
deconv_Thomas <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
  dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%
  dplyr::rename_with(~str_replace(.,"__", "_"))#! fix naming of deconv results

load( "/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meyloma_ludo/meyloma.RData")
truth_Thomas <- as_tibble(FACS_Thomas_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))

@@

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_Thomas <- list()
dict_Thomas[["BPRNACan"]] <- list(CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     NK = c("NK"))

dict_Thomas[["BPRNACanProMet"]] <- dict_Thomas[["BPRNACan"]]
dict_Thomas[["BPRNACan3DProMet"]] <- dict_Thomas[["BPRNACan"]]

dict_Thomas[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells") #"NKT.cells"?
                                     )

dict_Thomas[["CBSX_LM22"]] <- list(CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"), # "T.cells.follicular.helper", "T.cells.gamma.delta", "T.cells.regulatory..Tregs."?
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells.resting", "NK.cells.activated"))

dict_Thomas[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells"))

dict_Thomas[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = NULL)

dict_Thomas[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
                                   CD8 = c("T.cell.CD8+"),
                                   NK = c("NK.cell"))

@@

corr <- benchmark_corrplots(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_Thomas, key = "Samples", title = "test")
corr
```

>>>>

# Nakamura2018 RNAseq #! Change name!
## Data loading
```{r}
deconv_Nakamura2018 <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
  dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%
  dplyr::rename_with(~str_replace(.,"__", "_"))#! fix naming of deconv results

load( "/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meyloma_ludo/meyloma.RData")
truth_Nakamura2018 <- as_tibble(FACS_Nakamura2018_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))

@@

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_Nakamura2018 <- list()
dict_Nakamura2018[["BPRNACan"]] <- list(CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     NK = c("NK"))

dict_Nakamura2018[["BPRNACanProMet"]] <- dict_Nakamura2018[["BPRNACan"]]
dict_Nakamura2018[["BPRNACan3DProMet"]] <- dict_Nakamura2018[["BPRNACan"]]

dict_Nakamura2018[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells") #"NKT.cells"?
                                     )

dict_Nakamura2018[["CBSX_LM22"]] <- list(CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"), # "T.cells.follicular.helper", "T.cells.gamma.delta", "T.cells.regulatory..Tregs."?
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells.resting", "NK.cells.activated"))

dict_Nakamura2018[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = c("NK.cells"))

dict_Nakamura2018[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     NK = NULL)

dict_Nakamura2018[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
                                   CD8 = c("T.cell.CD8+"),
                                   NK = c("NK.cell"))

@@

corr <- benchmark_corrplots(deconv_data = deconv_Nakamura2018, true_estimates = truth_Nakamura2018, dict = dict_Nakamura2018, key = "Samples", title = "test")
corr
```
